---
title: "Box plot"
output:
  pdf_document: default
  html_notebook: default
---

Esta análise é feita spbre os dados da Azul Marinho, constantes da planilha "Cultivo.gsheet", contidos na aba Biomassa. Os dados foram exportados como Cultivo - Biomassa.csv

###Preparando os dados

```{r}
Biomassa <- read.csv(file = "Cultivo - Biomassa.csv", header = T)

# transformando algumas variáveis em fatores
Biomassa$viveiro = factor(Biomassa$viveiro, levels = c(1,2,3,4), labels = c("V1","V2","V3","V4"))

Biomassa$ciclo = factor(Biomassa$ciclo,levels = c(1,2,3,4,5,6,7,8,9,10), labels = c("C1","C2","C3","C4","C5","C6","C7","C8","C9","C10"))

Biomassa$ano = factor(Biomassa$ano)
Biomassa$bionutri = factor(Biomassa$bionutri)

str(Biomassa)
```

```{r}
library(ggplot2)

# Basic plot (sobrevivência vs bionutri)

p <- ggplot(Biomassa, aes(x = bionutri, y = sobrevivência)) +
  geom_boxplot()
p
```

```{r}
# Notched box plot
ggplot(Biomassa, aes(x = bionutri, y = sobrevivência)) +
  geom_boxplot(notch = TRUE)
```

###The function stat_summary() can be used to add mean points to a box plot :

```{r}
# Box plot with mean points
p + stat_summary(fun.y = mean, geom = "point", size = 2, col = "red")
```

## Box plot with dots
Dots (or points) can be added to a box plot using the functions geom_dotplot() or geom_jitter() :

```{r}
# Box plot with dot plot
p + geom_dotplot(binaxis = "y", stackdir = "center", dotsize = 1)
# Outra alternativa
p + geom_point()

# Box plot with jittered points
# 0.2 : degree of jitter in x direction
p + geom_jitter(shape = 16, position = position_jitter(0.2))

# Outra alternativa  if you want to mess with tranparency.
p + geom_jitter() + geom_boxplot(alpha = 0.7) 
```

##Change box plot colors by groups
###Change box plot line colors

```{r}
# change box plot lines colors by gorup
p <- ggplot(Biomassa, aes(x = bionutri, y = sobrevivência, color = bionutri)) +
  geom_boxplot() + geom_jitter()
p
```
It is also possible to change manually box plot line colors using the functions :

scale_color_manual() : to use custom colors
scale_color_brewer() : to use color palettes from RColorBrewer package
scale_color_grey() : to use grey color palettes

```{r}
# Use custom color pallets
p+scale_color_manual(values=c("#999999", "#E69F00"))
# Use brewer color palettes
p+scale_color_brewer(palette="Dark2")
# Use grey scale
p + scale_color_grey() + theme_classic()
```

###Change box plot fill colors
In the R code below, box plot fill colors are automatically controlled by the levels of bionutri:

```{r}
# Use single color
ggplot(Biomassa, aes(x = bionutri, y = sobrevivência,)) +
  geom_boxplot(fill = '#A4A4A4', color = "black") +
  theme_classic()

# Change box plot colors by groups
ggplot(Biomassa, aes(x = bionutri, y = sobrevivência, fill = bionutri)) + geom_boxplot()
```

It is also possible to change manually box plot fill colors using the functions :

scale_fill_manual() : to use custom colors
scale_fill_brewer() : to use color palettes from RColorBrewer package
scale_fill_grey() : to use grey color palettes

```{r}
# Use custom color palettes
p+scale_fill_manual(values=c("#999999", "#E69F00"))
# use brewer color palettes
p+scale_fill_brewer(palette="Dark2")
# Use grey scale
p + scale_fill_grey() + theme_classic()
```

###Change the legend position

```{r}
p + theme(legend.position = "top")
p + theme(legend.position = "bottom")
p + theme(legend.position = "none") # Remove legend
```

###Box plot with multiple groups
####Por viveiro (neste exemplo)

```{r}
# Change box plot colors by groups
ggplot(Biomassa, aes(x = bionutri, y = sobrevivência, fill = viveiro)) +
  geom_boxplot()
# Change the position
p <- ggplot(Biomassa, aes(x = bionutri, y = sobrevivência, fill = viveiro)) + geom_boxplot(position = position_dodge(1))

p
```

###Customized box plots

```{r}
# Basic box plot
ggplot(Biomassa, aes(x = bionutri, y = sobrevivência,)) +
  geom_boxplot(fill = "gray") +
  labs(title = "Sobrevivência por Probióticos", x = "Probiótico", y = "Sobrevivência (%)") + theme_classic()

# Change  automatically color by groups

bp <- ggplot(Biomassa, aes(x = bionutri, y = sobrevivência, fill = bionutri)) + geom_boxplot() +
  labs(title = "Sobrevivência por Probióticos", x = "Probiótico", y = "Sobrevivência (%)", caption = "Azul Marinho")
bp + theme_classic()
bp + labs(fill = "Probiótico") # Muda o título da legenda
```

##Gráfico Final

```{r}
library(ggthemes)
bp <- ggplot(Biomassa, aes(x = bionutri, y = sobrevivência, color = bionutri)) + geom_boxplot() + geom_jitter(position = position_jitter(0.2)) +
  labs(title = "Sobrevivência por Probióticos\n2015-2017", x = "Probiótico", y = "Sobrevivência (%)", caption = "Azul Marinho")
bp + theme_classic()
bp + labs(color = "Probiótico") # Muda o título da legenda para Probiótico
```

